\section{Referencias}
\begin{thebibliography}{9}
\bibitem{pagano} 
Pagano, M., Panetta, F., Zingales, L. 
\textit{ Why do companies go public?: An empirical
analysis.}
The Journal of Finance (1998), 27-64.

\iffalse
\bibitem{wework} 
Erik Sherman. 
\textit{The Pain From WeWork’s Failed IPO Deepens as Bondholders Get Stuck Underwater}.
Fortunne, 2019.
url: \url{https://fortune.com/2019/11/12/wework-failed-ipo-bonds-underwater/}
 

\bibitem{sec} 
U. S. Securities and Exchange Commission. 
\textit{SEC Proposes to Update Accredited Investor Definition to Increase Access to Investments}.
U. S. Securities and Exchange Commission, 2019.
url: \url{https://www.sec.gov/news/press-release/2019-265}
\fi

\bibitem{utility}
BitcoinWiki. 
\textit{Utility token}.
BitcoinWiki, 2019.
url: \url{https://en.bitcoinwiki.org/wiki/Utility_token}

\bibitem{fungible} 
Merriam-Webster. 
\textit{Fungible}.
Merriam-Webster, 2019.
url: \url{https://www.merriam-webster.com/dictionary/fungible}


\bibitem{eips20} 
Fabian Vogelsteller, Vitalik Buterin. 
\textit{EIP 20: ERC-20 Token Standard}.
Ethereum Improvement Proposals, 2019.
url: \url{https://eips.ethereum.org/EIPS/eip-20}

\iffalse
\bibitem{peruvian} 
Pulso. 
\textit{Inversionistas internacionales adquieren el 100\% de Peruvian Airlines}.
LTPulso, 2019.
url: \url{https://www.latercera.com/pulso/noticia/inversionistas-internacionales-adquieren-100-peruvian-airlines/856170/}
\fi

\bibitem{erc1400} 
The Security Token Standard. 
\textit{Security Token Standard}.
The Security Token Standard, 2019.
url: \url{https://thesecuritytokenstandard.org/}

\bibitem{stablecoin} 
Binance. 
\textit{Stablecoin}.
Binance Academy, 2019.
url: \url{https://www.binance.vision/glossary/stablecoin}

\bibitem{eip1108} 
Antonio Salazar Cardozo, Zachary Williamson
\textit{EIP 1108: Reduce alt\_bn128 precompile gas costs}.
Ethereum Improvement Proposals, 2019.
url: \url{https://eips.ethereum.org/EIPS/eip-1108}


\bibitem{web3} 
web3.js
\textit{web3.js - Ethereum JavaScript API}
web3.js, 2019.
url: \url{https://web3js.readthedocs.io/en/v1.2.4/}

\bibitem{ECDA} 
Svetlin Nakov
\textit{ECDSA: Elliptic Curve Signatures}
Practical Cryptography for Developers, 2019.
url: \url{https://cryptobook.nakov.com/digital-signatures/ecdsa-sign-verify-messages}
\end{thebibliography}

